GIT commands

1) Initial Git :  
git init
initialized  empty git repostry

2) local changes -> staged changes
git add filepath
git add.

3) commit
 git commit -m 'message'


PS C:\Users\USER\Desktop\FRONT END> node "c:\Users\USER\Desktop\FRONT END\git.js"
PS C:\Users\USER\Desktop\FRONT END> git init
Initialized empty Git repository in C:/Users/USER/Desktop/FRONT END/.git/
PS C:\Users\USER\Desktop\FRONT END> git add git.js (file name)
PS C:\Users\USER\Desktop\FRONT END> git config --global user.name "Rohit kumar"
PS C:\Users\USER\Desktop\FRONT END> git config --global user.email "rk4818294@gmail.com"
PS C:\Users\USER\Desktop\FRONT END> git commit -m "js file created"
[master (root-commit) d8e2f8f] js file created
 1 file changed, 2 insertions(+)


git add.
 git commit -m 'message'
 git push



 to push changes to server - git push -u origin <branch_name>

merge-
git checkout main
git merge origin/Sec.Branch.name
git push


PS C:\Users\USER\Desktop\FRONT END> git init
Reinitialized existing Git repository in C:/Users/USER/Desktop/FRONT END/.git/
PS C:\Users\USER\Desktop\FRONT END> git add .
PS C:\Users\USER\Desktop\FRONT END> git commit -m "PROJECT"
[main f0d5df4] PROJECT
 1 file changed, 0 insertions(+), 0 deletions(-)
 create mode 100644 Git/Assessment.html
PS C:\Users\USER\Desktop\FRONT END> git push
To https://github.com/rk4818294-code/frontend.git
 ! [rejected]        main -> main (fetch first)
error: failed to push some refs to 'https://github.com/rk4818294-code/frontend.git'
hint: Updates were rejected because the remote contains work that you do not
hint: have locally. This is usually caused by another repository pushing to
hint: the same ref. If you want to integrate the remote changes, use
hint: 'git pull' before pushing again.

PS C:\Users\USER\Desktop\FRONT END> git push -u origin main
branch 'main' set up to track 'origin/main'.
Everything up-to-date
PS C:\Users\USER\Desktop\FRONT END> 


**********************************************************************************************************************************************


Imp Question :

10 marks >>>>>>>>>>>>>>

Create bootstrap grid which have 2 responsive card that appears side by side on large screen and stack vertically on small screen.

Explain git commands to merge one branch to another branch and also explain the merge operation.

Create responsive web page using grid that display 3 cards in a row on large screen and 1 card per row in small screen.

Git command to create a branch, switch the branch, merge into main, push to GitHub, and explain the concept of branching.

Command to clone a repo, create a new file, commit the changes, push them to repo.

6 marks >>>>>>>>>>>>>>

Build HTML code to create a responsive card with image, title, and description with an example.

Explain the purpose of .gitignore file with an example.

Write steps to clone a repo from GitHub and list repo files.

Write a Bootstrap code to create a navbar and link Home, Contact, Service.