PAPER QUESTIONS ( HTML )

10 marks


1.      CREATE PORTFOLIO USING LIST, IMAGE, TABLE, ANCHOR TAG.                                                                      DONE        
2.	    MAKE UNORDERED LIST OF UR CHOICE STYLE THE LIST TO SQUARE BULLET WITH GREEN COLOUR                                          DONE 
3.	    CREATE HTML FORM WITH USERNAME AND PASSWORD STYLE THE FORM USING CSS BACKGROUND LIGHTGREY PADDING MARZIN.                   DONE 
4.	    EXPLAIN HTML FORMS ELEMENTS                                                                                                 DONE                                 
5.	    EXPLAIN CSS FLEXBOX                                                                                                         DONE
6.	    EXPLAIN GRID SYSTEM DIAGRAM WITH CODE                                                                                       DONE
7.	    CSS SLECETORS, NESTED LIST, RADIO,CHECKBOX, FORM, GRID, FLEXBOX                                                             DONE             

--------------------------------------------------------------------------------------------------------------------------------------------

6 marks

7.      Explain inline, internal, and external CSS.                                                                                DONE
8.      Explain gradients in CSS.                                                                                                  DONE       
9.      Explain four types of CSS selectors.                                                                                       DONE                                                                                                                                                                                                   
---------------------------------------------------------------------------------------------------------------------------------------------

*** previous imp ques**** 

1.         write a html code to create a form with fields name email gender  favorite subject and submit button                     DONE 
2.         write a nested list of your choice                                                                                       DONE                                                                      
3.         build a div give it a solid red color border with equal margin and padding of your choice                                DONE      
4.         construct an html page that display  3 image with each acting as a link to a different website                           DONE        
5.         make use of differnt type of CSS selectors with example like universal , id, class                                       DONE              
6.         write an html code to display an image with a border of red color with width of 500px                                    DONE 

10 MARKS  

1.       You have to create a portfolio website.Include:List,Image,Table,Anchor tag                                                DONE
3.       Make a list of your choice.Style the list using square bullets and provide green color.                                   DONE
4.       You have to create one HTML form with:Username,Password,Style the form using CSS.                                         DONE
5.       Explain all HTML form elements.                                                                                           DONE
6.       Explain CSS Flexbox in detail.                                                                                            DONE
7.       Explain Grid system with diagram and explanation.                                                                         DONE
10.      Explain: CSS selectors,Radio button,Checkbox,Form elements                                                                DONE                                                            

---------------------------------------------------------------------------------------------------------------------------------------------                                                                                        DONE

***previous question***

HTML

Important Questions Discussion

2 Marks

Q1. HTML comments are written as?
→ <!-- -->
Q2. HTML stands for?
→ HyperText Markup Language
Q3. Tag which contains a page title is?
→ Head → Title tag
Q4. Symbol for ID selector is?
→ #
Q5. Property for font family is?
→ font-family
Q6. Identify which attribute is used to open a link in a new tab.
→ target="_blank"


6 Marks

Q1. Explain RGB hex code format with example.                                                                                         DONE
Q2. Experiment with absolute and relative units in CSS with example.                                                                  DONE
Q3. Write HTML code to create a table showing students’ details with columns:Roll No, Name, Marks, Grade. (Use at least four rows.)   DONE                                                                         
Q4. Explain box model properties with a diagram.                                                                                      DONE
Q5. Construct an HTML page that displays three images, with each image acting as a link to a different website.                       DONE
Q6. Build a div and give it a solid red coloured border with equal margin and padding of your choice.                                 DONE


10 Marks

Q1. Write HTML code to create a form with fields:Name, Email, Gender, Favourite Subject and Submit button.                             DONE
Q2. Make use of different types of CSS selectors with example:Universal, Element, Class and ID.                                        DONE
Q3. Write a nested list of your choice.                                                                                                DONE
Q4. Write a portfolio website which includes image, list, table and anchor.                                                            DONE
Q5. Build two div and style them using class and id selector.Apply font colour, background colour, margin and padding of your choice.  DONE
Q6. Write HTML code to display an image with a red coloured border and a width of 500pX.                                               DONE

-------------------------------------------------------------------------------------------------------------------------------------------------



                            JAVA SCRIPT

1     PROGARM TO FIND THE 2ND LARGEST NUMBER IN A ARRAY USING JS.                                            DONE
2.    CREATE A PROGRAM TO COUNT EACH ELEMENT AND ITS OCCURANCE (frequency).                                  DONE
3.	  MERGE 2 SORTED ARRAY INTO 1 SORTED ARRAY .                                                             DONE
4.    PRINT EVEN NUMBER UPTO 100 WITH FOR LOOP .                                                             DONE
5.    EXPLAIN DIFFERNCE BETWEEN == AND ===.                                                                  DONE
6.	  EXPLIAN STRING AND ARRAY METHOD                                                                        DONE
7.	  EXPLAIN DATATYPES IN JS                                                                                DONE
8.    Explain 3 types of functions.                                                                          DONE
9.    Explain let, var, and const.                                                                           DONE
